REDO Simulating Dwarf Galaxy Evolution with Individual Star Feedback and Chemical Evolution I: Methods and Test Case

### 2017-10-18 main.tex
Update on Overleaf.

\section{Methods}
\label{sec:methods}
In brief, we produce high resolution galaxy scale simulations tracking stars not as SSP's, but as individual stars sampled from an assumed IMF.
This allows us to follow star-by-star variations in feedback physics and stellar yields in detail. To properly model the ISM, we track non-equilibrium primordial chemistry (including molecular hydrogen) using \texttt{Grackle} \citep{GrackleMethod}, with heating and approximate self-shielding from a metagalactic UV background. We use updated \texttt{Cloudy} metal line cooling tables consistent with our self-shielding approximation, and an updated observationally motivated dust model for the low metallicity regimes studied here (Z $\lesssim 0.1$ Z$_{\odot}$). Each star is assigned basic properties (surface gravity, effective temperature, radius, lifetime) from tabulated stellar evolution models, which inform how the stars deposit their feedback. We directly track ionizing radiation from massive stars using an adaptive ray tracing radiative transfer method that includes the effects of radiation pressure. In addition, we follow the optically thin non-ionizing UV radiation from these stars leading to photoelectric heating and Lyman-Werner (LW) dissociation of molecular hydrogen. We track the stellar wind feedback and supernovae from these stars, depositing individual metal yields from both. We include AGB wind feedback and yields for lower mass stars, and track these directly as Type Ia supernovae progenitors. We follow yields for 12 individual metal species, chemically tagging each star with the associated local gas abundances for each species. These methods are discussed in detail below.

\subsection{Hydrodynamics and Gravity}

@@

The computational domain in an AMR simulation is adaptively refined up to a designated resolution limit for a given set of refinement criteria. We require that the Jeans length be resolved by a minimum of 8 cells, continually refining a given region until this criteria is met or the region reaches the maximum resolution. Our maximum resolution in the initial comparison simulations presented here is 2.5 pc, but our peak resolution in our fiducial set of lower mass galaxies is 1.5~pc (see Emerick et. al. in prep). At maximum resolution, the Jeans length can become under resolved, leading to artificial numerical fragmentation. Studies have shown that resolving the Jeans length by at least 4 cells is required to suppress this fragmentation \citep{Truelove1997}.

We set the star formation density threshold to the point which the Jeans length becomes resolved by only 4 cells in sub-200 K gas, or about 200 \ccunit (as discussed further in Section~\ref{sec:star formation}). Forming stars from this gas will reduce the local density, ensuring the Jeans length is resolved. However, since star formation is not instantaneous, we employ a pressure floor to support gas against artificial collapse once its Jeans length becomes unresolved. This prevents dense, self-gravitating gas from rapidly reaching densities significantly above our resolution limit.

@@

We use the chemistry and cooling library \texttt{Grackle}\footnote{https://grackle.readthedocs.io/en/grackle-3.0/} v 3.0 to follow a nine species non-equilibrium chemistry network (H, H$^+$, He, He$^+$, He$^{++}$, e$^{-}$, H$_2$, H$^{-}$, and H$_{2}$) which includes radiative heating and cooling from these species and metals.\footnote{We use a slightly modified version of the the main \texttt{Grackle} repository, available at https://bitbucket.org/aemerick/grackle-emerick at changeset 59adc76b3130.} \texttt{Grackle} is a freely available, open source multi-code library, designed to interface with a wide variety of astrophysical codes. We outline specific model choices made in our simulations and refer the reader to \citep{GrackleMethod} for a detailed discussion of the code. We apply the \cite{Glover2008} three body rate for H$_{2}$ formation and include a model for H$_2$ formation on dust, dust heating, and dust cooling following the methods in \citet{2000ApJ...534..809O} and {2005ApJ...626..627O} as included in \texttt{Grackle}. However, we update the default dust to gas ratio scaling in \texttt{Grackle} to account for the steeper scaling in low metallicity regimes ($Z \lesssim 0.1 Z_{\odot}$) with the broken power law scalings from \cite{Remy-Ruyer2014}. For metallicities above $\sim 0.1 Z_{\odot}$, this is equivalent to the the default behavior in \texttt{Grackle}.

Metal line cooling is modeled using pre-computed \texttt{Cloudy}\footnote{http://www.nublado.org/} tables interpolated as a function of density, temperature, and redshift, using the \cite{HM2012} UV metagalactic background. As discussed in more detail in Section~\ref{sec:diffusive heating}, we account for approximate self-shielding of H and He against this UV background. Using this prescription with metal line cooling tables computed under an optically thin assumption can lead to an order of magnitude overestimation of the cooling rate at certain densities. We use re-computed metal line tables consistent with the self-shielding approximation. Our effective cooling curve and these new tables are publicly available in the main \texttt{Grackle} repository. These are both discussed in greater detail in Appendix ~\ref{appendix:cooling}.

@@

We make the common ansantz that star formation occurs by converting some fraction of gas into stars in a free fall time ($\tau_{\rm ff}$) as characterized by a star formation efficiency, $\epsilon_{\rm f} \simeq 0.02$. At high resolution, one's choice of $\epsilon_{\rm f}$ is irrelevant \citep{Orr2017, FIRE2}, as star formation is ultimately self-regulated by feedback.
%but we find that $\epsilon_{\rm f}$ may impact star formation in the lowest mass halos, which are unusually sensitive to stellar ionization feedback (see Emerick et. al. in prep).
The the gas mass converted to stars in a time step, $dt$, is
\begin{equation}
M_{ {\rm gas} \to *} = \epsilon_{\rm f} M_{\rm gas} \frac{dt}{\tau_{\rm ff}}.
\end{equation}
In practice, $dt/\tau_{\rm ff} \ll 1$, and $M_{ {\rm gas} \to *}$ is smaller than the minimum star particle mass at parsec scale resolution. We therefore allow star formation to proceed stochastically, following the methods in \cite{Goldbaum2015, Goldbaum2016}, modified for variable stellar masses. In each cell that could potentially form stars, we compute the probability that 100 M$_{\odot}$ of gas will be converted into stars in that time step, and use a random number draw to determine whether or not star formation actually occurs. If it does, we random sample over the adopted IMF until 100 M$_{\odot}$ of stars form, keeping last sampled particle if the total stellar mass formed exceeds 100 M$_{\odot}$. We make the simple assumption of a Salpeter IMF \citep{Salpeter1955} with $\alpha = 2.35$, sampling over a minimum stellar mass of 1 M$_{\odot}$ and maximum stellar mass of 100 M$_{\odot}$.

Formed stars are deposited with random positions within the star forming cell and assigned velocities equal to the cell bulk velocity with a 1~km~s$^{-1}$ velocity dispersion. Stars are assigned metallicities corresponding to the metallicity of the star forming zone, and are chemically tagged with the 14 individual species abundances (H, He, and the 12 metals) we follow in our simulations. Stars evolve throughout the simulation, losing mass from stellar winds and supernovae as described below, and by changing types, but persist throughout the entire simulation. For example, low mass stars are tagged as white dwarfs at the end of their life, which may eventually explode as a Type Ia supernova (discussed below), after which they persist as massless tracer particle ``remnants''.

@@

Following the initialization procedure of \cite{Hu2017}, we use artificial supernova driving to generate realistic densities and turbulent properties in the galaxy ISM. This additionally prevents an otherwise uniform collapse of the gas disk. The supernovae explode at a fixed rate of $0.4$~Myr$^{-1}$, corresponding to the SFR obtained given the central HI surface density and the relation presented in \citep{Roychowdhury2009}. We stop the artificial driving 25~Myr after the first star particle forms. These artificial supernova do not drive chemical evolution of the galaxy, containing metal yields corresponding to the mean ISM abundances.

@@

\subsection{Morphological Structure}
\label{sec:structure}
We show edge-on (left) and face-on (right) projections of our fiducial galaxy (top) and shortrad (bottom) at the end of the simulation time in Figure~\ref{fig:panel}. The left two panels are number density weighted projections through the full disk, giving HI and H$_2$ column density. The right hand panels show face-on projections through thin (50 pc) slabs at the center of the galaxy for the interstellar radiation field normalized to the MW value in the solar neighborhood, or $G_o$, and gas temperature. In general, the shortrad simulation is visually consistent with that found in \citep{Hu2016,Hu2017}, exhibiting a thick, puffy disk with a relatively smooth HI column and an H$_2$ distribution that is more confined to the plane of the galaxy and is roughly uniformly distributed. Looking at the fiducial simulation, it is clear that the ray-tracing radiative transfer produces a significant change in the galactic structure. Both the HI and H$_2$ are significantly more disturbed, with notable gaps in the HI column caused by regions carved out by the ionizing radiation, and with significantly less uniform H$_2$ column, from molecular hydrogen destroyed through ionization heating.

%\begin{figure}
%\includegraphics[width=0.9\linewidth]{panel/sndriving_particles}\\
%\vspace{0.1cm}
%\includegraphics[width=0.9\linewidth]{panel/shortrad_particles}
%\caption{Face on, density weighted projections of gas number density for both galaxies. Each of the black points represents a single particle (star) in the simulation, and can be a living star, a white dwarf, a massless tracer originating from a Type Ia explosion, or a SNII remnant. The population is dominated by low mass stars; only a fraction of these particles have active feedback (winds, radiation, supernovae) at any one moment. \textbf{yes plot fonts and label sizes need fixing - AE}}
%\label{fig:number density}
%\end{figure}

The differences are further emphasized in the temperature projections, where a visually more significant fraction of the gas in the fiducial simulations sits at temperatures near 10$^4$~K, and much less sits at very low ($\sim$ 10 K) temperatures. The differences between gas phase in these simulations is discussed in Section~\ref{sec:phase}. The ISRF of both galaxies is quite similar, though since the ISRF in our model is generated by massive stars alone, it reflects the SFR over the previous 10 - 40 Myr, which is in fact similar in both galaxies (see Section~\ref{sec:sfr}).

Finally, in Figure~\ref{fig:number density} we present face-on projections of gas number density in both galaxies, marking each star particle in the simulation with an individual black point. Although the particles obscure some of the structure in the disk, the same general differences noted above are visible here. In particular, the fiducial simulation has significantly more disturbed gas morphology with larger regions of low density gas, and less dense gas structures.

@@

@@

In Figure ~\ref{fig:SFR} we compare the star formation rates of both simulations (left), along with the stellar mass evolution (middle), and HI mass evolution (right). The peak and average SFRs for each galaxy over the 270~Myr simulation time are comparable, with a peak at roughly $0.04$~M$_{\odot}$~yr$^{-1}$ and an average of about $1.1~\times~10^{-3}$~M$_{\odot}$~yr$^{-1}$ in each simulation. However, the SFR evolution is qualitatively different, with the fiducial run exhibiting a $\sim$80~Myr period of minimal, patchy star formation between 125~Myr and 200~Myr ($<\rm{SFR}>~=~2.2\times~10^{-5}~$M$_{\odot}$~yr$^{-1}$). Although there is a lull in star formation during this time in the shortrad case, star formation is continuous. This difference is due solely to the long-range effects of stellar ionizing radiation, though we cannot also rule out the possibility that it also makes SN feedback more effective. It is apparent in this simulation that stellar radiation feedback is effective at suppressing star formation galaxy wide, not just locally.

%\begin{figure}
%\includegraphics[width=0.9\linewidth]{HI_surface_density}
%\caption{\textbf{Coloring / style needs to change} Time averaged HI surface density profiles (dashed line) for both galaxies over the simulation time. The hatched regions show one standard deviation from the mean in each radial bin. Although there is noticeable variance in the HI profile in both galaxies, it is significantly greater for the full physics simulation. Truncating the ionizing photons to local regions alone results in a steadier and on average greater amount of HI at all but the very outer edge of the galaxy.}
%\label{fig:HI profile evolution}
%\end{figure}

The long-range effects of the ionization are clear in the HI evolution of these galaxies (middle). The presence of stellar ionizing radiation throughout the galaxy decreases the amount of HI gas present in the disk by a factor of $\sim$4, by the end of the simulation time. Figure~\ref{fig:HI profile evolution} shows the average HI surface density profile of each galaxy over the course of the simulation time, with the filled regions indicating one standard deviation from the mean. These differences in evolution lead to differences in metal production and distribution in these two galaxies, discussed further in \ref{sec:chemical evolution}.

@@

Show mass loading factors as a function of time here at all radii.

@@

Detailed outflow properties, beyond outflow rates and mass loading factors, are important discriminators between the model dependent feedback physics included in galaxy simulations. (this has been shown previously with XX XX XX producing very different outflow properties depending on what physics is included). In Figure~\ref{fig:outflow_velocity} we present radial velocity distributions of all material outside our dwarf galaxy's disk, and within the halo, broken into three gas phases. Half of the outflow, by mass, is at velocities below 40 km s$^{-1}$, with 75\% at velocities of 70 km s$^{1} or below. This gas is dominated by the two warm gas phases, with the WNM dominating at lower velocities, and the WIM at higher velocities. The distribution has a very long tail out to and beyond 500 km s$^{-1}$. These dominant launching mechanism in this simulation are supernovae (Emerick et. al. in prep), generating a rapidly moving and volume filling HIM. However, as shown the HIM comprises very little of the outflow by mass. Most of the outflowing gas comes from the warm phase, pushed out by the high pressure, fast moving HIM. Some of this warm gas certainly originates from adiabatically and radiatively cooled HIM, however. The amount of transfer between phases in the halo of our galaxy will be investigated in future work.

@@

\begin{figure*}
\includegraphics[width=0.45\linewidth]{phase_diagram.png}
\caption{The full-box temperature vs. number density phase diagram of our dwarf galaxy simulation, averaged over the final 50 Myr of simulation time.}
\label{fig:phase}
\end{figure*}

@@

\begin{figure*}
\includegraphics[width=0.45\linewidth]{mass_fraction_evolution.png}
\includegraphics[width=0.45\linewidth]{volume_fraction_evolution.png}
\caption{The evolution of the mass and volume fractions for each phase of our galaxy's ISM. This figures only consider gas present within the disk of the galaxy.}
\label{fig:ISM_evolution}
\end{figure*}

\subsection{Chemical Evolution} %and Metal Enriched Outflows}
\label{sec:chemical evolution}
Although our simulations are long enough to begin to discuss morphological and dynamical differences between the galaxies, they are too short to focus in detail in chemodynamical evolution. For this reason, we make only a brief comparison between these two galaxies, saving a more detailed examination for our simulations of lower mass dwarf galaxies run for $\sim$Gyr timescales (Emerick et. al. in prep).

%\begin{figure}
%\includegraphics[width=0.9\linewidth]{element_mass_comparison_fraction}
%\caption{Ratio of amount of mass in a given mutually exclusive phase (disk, halo, and stars) between the fiducial and shortrad simulations. The halo ratio has been multiplied by 0.5 for clarity. We caution against making any interpretation of Mn and ratios for the s and r-process elements (Y, Ba, and Eu) as there is very little mass of these elements produced in the $\sim$100 Myr timescales examined here. \textbf{comment: I thought of a few different ways of conveying this information, but all were painful to look at or make (e.x. double bar graph showing fractional element dist)... this was the least painful, but open to suggestions}.}
%\label{fig:element mass ratio}
%\end{figure}

In Figure~\ref{fig:element mass ratio} we divide the total mass of each element contained in each of three regimes (stars, disk, or halo) of the fiducial simulation by the mass in the shortrad simulation (i.e. $>$ 1 means more mass in the given in the given phase in the fiducial simulation). We multiply the halo ratio, defined as all elements outside the disk but within the virial radius, by 0.5 for clarity. Although the total metal production in each galaxy is similar, the partitioning of those metals differs significantly.

The fiducial simulation contains more (by a factor of 3 to 5) mass in a given species in the halo than the shortrad simulation. The additional feedback produced by tracing radiation outside 50 pc from each stars effectively drives gas and metals out of the disk. Most of this gas driven into the halo is still contained well within R$_{\rm vir}$ of this galaxy. It is unclear whether or not the additional feedback in the fiducial model will be able to move gas farther out into the halo. We note that a majority of the produced mass is still in the disk for each simulation, which is why the disk ratios are around unity. Though it varies for each element, the halo masses represent 10-20\% of the disk mass for the fiducial simulation, and 3-5\% for the shortrad simulation.

The feedback differences also impact the stellar metal abundance evolution in each galaxy. On average, the total mass of each element locked away in stars in the shortrad simulation is roughly twice as much as that contained in stars in the fiducial simulation. This is somewhat surprising because not only does the fiducial simulation have a slightly greater stellar mass by the end of the 270 Myr run time (2 $\times$ 10$^4$ M$_{\odot}$), but it also forms more of its stars later than the shortrad simulation. Naively, this should mean there would be more mass in a given element locked in the fiducial simulation stars as it has both more mass in stars and there has been slightly more time for produced metals to mix with the ISM and into these stars. This implies that differences in feedback evolution can lead to potentially significant differences in stellar abundances.

We caution against any interpretation of the ratio for Mn and the ratios for the s-process and r-process elements (Y, Ba, and Eu) as there is very little mass in these species in either simulation. However, we do point out that the ratios for N are qualitatively different than each other element. There is more N in the shortrad disk than the fullrad and its ratios are all much closer to unity than any other element. We suspect this is because, at these low metallicities, the IMF weighted N production is dominated by stellar winds of massive stars around $8 - 10$~M$_{\odot}$ and AGB stars\footnote{Although AGB stars are less relevant on these timescales. The lifetime of a 5 M$_{\odot}$ star at these metallicities is on order of 100 Myr} . However, IMF weighted production for the other species are dominated by SNe. This means most of the N produced is injected in a wind phase. This is more easily retained and mixed in the ISM than the other elements which are injected with much higher energy in SNe. These initial results immediately suggest that differences in both included feedback and mechanisms for yield injection can create discernible differences in stellar abundance patterns. How abundance variations like this evolve over longer timescales in lower mass dwarf galaxies is the subject of ongoing work (Emerick et. al. in prep.).

\textbf{I did have a panel plot showing column for each element here, but decided to take it out. Might be worth putting in panel comparison for a few elements, but not sure. Suggestions? - AE}
%\begin{figure*}
%\includegraphics[width=0.9\linewidth]{DD0204_elements}
%\caption{Panel plot of elements \textbf{PLACEHOLDER FOR NOW}}
%\label{fig:elements panel}
%\end{figure*}

>>>>

\section{Methods}
\label{sec:methods}
In brief, we produce high resolution galaxy scale simulations tracking stars not as SSP's, but as individual stars sampled from an assumed IMF.
This allows us to follow star-by-star variations in feedback physics and stellar yields in detail. To properly model the ISM, we track non-equilibrium primordial chemistry (including molecular hydrogen) using \texttt{Grackle} \citep{GrackleMethod}, with heating and approximate self-shielding from a metagalactic UV background. We use updated \texttt{Cloudy} metal line cooling tables consistent with our self-shielding approximation (see Appendix ~\ref{appendix:cooling}), and an updated observationally motivated dust model for the low metallicity regimes studied here (Z $\lesssim 0.1$ Z$_{\odot}$). Each star is assigned basic properties (surface gravity, effective temperature, radius, lifetime) from tabulated stellar evolution models, which inform how the stars deposit their feedback. We directly track ionizing radiation from massive stars using an adaptive ray tracing radiative transfer method that includes the effects of radiation pressure. In addition, we follow the optically thin non-ionizing UV radiation from these stars leading to photoelectric heating and Lyman-Werner (LW) dissociation of molecular hydrogen. We track the stellar wind feedback and supernovae from these stars, depositing individual metal yields from both. We include AGB wind feedback and yields for lower mass stars, and track these directly as Type Ia supernovae progenitors. We follow yields for 15 individual metal species (C, N, O, Na, Mg, Si, S, Ca, Mn, Fe, Ni, As, Sr, Y, and Ba), chemically tagging each star with the associated local gas abundances for each species. These methods are discussed in full detail below.

\subsection{Hydrodynamics and Gravity}
\label{sec:hydro}

@@

The computational domain in an AMR simulation is adaptively refined up to a designated resolution limit for a given set of refinement criteria. We require that the Jeans length be resolved by a minimum of 8 cells, continually refining a given region until this criteria is met or the region reaches the maximum resolution. Our maximum resolution in the simulations presented here is 1.8 pc. At maximum resolution, the Jeans length can become under resolved, leading to artificial numerical fragmentation. Studies have shown that resolving the Jeans length by at least 4 cells is required to suppress this fragmentation \citep{Truelove1997}.

We set the star formation density threshold to the point which the Jeans length becomes resolved by only 4 cells in sub-200 K gas, or about 200 \ccunit (as discussed further in Section~\ref{sec:star formation}). Forming stars from this gas will reduce the local density, ensuring the Jeans length is resolved. However, since star formation is not instantaneous, we employ a pressure floor to support gas against artificial collapse once its Jeans length becomes unresolved. This prevents dense, self-gravitating gas from rapidly reaching densities significantly above our resolution limit. The use of a pressure floor is common in galaxy scale simulations with limited dynamic range. (\textbf{I contrasted this to Hu's work which allows arbitrarily high densities, hoping feedback mitigates how high the densities actually get, but took it out. Leave it in?})

@@

We use the chemistry and cooling library \texttt{Grackle}\footnote{https://grackle.readthedocs.io/en/grackle-3.0/} v 3.0 to follow a nine species non-equilibrium chemistry network (H, H$^+$, He, He$^+$, He$^{++}$, e$^{-}$, H$_2$, H$^{-}$, and H$_{2}$) which includes radiative heating and cooling from these species and metals.\footnote{We use a slightly modified version of the the main \texttt{Grackle} repository, available at https://bitbucket.org/aemerick/grackle-emerick at changeset 59adc76b3130.} \texttt{Grackle} is a freely available, open source multi-code library, designed to interface with a wide variety of astrophysical codes. We outline specific model choices made in our simulations and refer the reader to \citep{GrackleMethod} for a detailed discussion of the code. We apply the \cite{Glover2008} three body rate for H$_{2}$ formation and include a model for H$_2$ formation on dust, dust heating, and dust cooling following the methods in \citet{2000ApJ...534..809O} and \citet{2005ApJ...626..627O} as included in \texttt{Grackle}. However, we update the default dust to gas ratio scaling in \texttt{Grackle} to account for the steeper scaling in low metallicity regimes ($Z \lesssim 0.1 Z_{\odot}$) with the broken power law scalings from \cite{Remy-Ruyer2014}. For metallicities above $\sim 0.1 Z_{\odot}$, this is equivalent to the the default behavior in \texttt{Grackle}. 
% Since we assume a dust abundance that depends only on metallicity, we do not track dust destruction or creation, which may play an important role regulating detailed ISM properties. (Vogelsberger is working on this directly but no papers yet... will cite if it gets submitted by then)

Metal line cooling is modeled using pre-computed \texttt{Cloudy}\footnote{http://www.nublado.org/} tables interpolated as a function of density, temperature, and redshift, using the \cite{HM2012} UV metagalactic background. As discussed in more detail in Section~\ref{sec:diffusive heating}, we account for approximate self-shielding of H and He against this UV background. Using this prescription with metal line cooling tables computed under an optically thin assumption can lead to an order of magnitude overestimation of the cooling rate at certain densities. To address this issue, we use re-computed metal line tables consistent with the self-shielding approximation.  We have made these new tables public in the main \texttt{Grackle} repository. These are both discussed in greater detail in Appendix ~\ref{appendix:cooling}.

@@

We make the common ansantz that star formation occurs by converting some fraction of gas into stars in a free fall time ($\tau_{\rm ff}$) as characterized by a star formation efficiency, $\epsilon_{\rm f} \simeq 0.02$. At high resolution, one's choice of $\epsilon_{\rm f}$ should be irrelevant \citep{Orr2017, FIRE2}, as star formation is ultimately self-regulated by feedback.
%but we find that $\epsilon_{\rm f}$ may impact star formation in the lowest mass halos, which are unusually sensitive to stellar ionization feedback (see Emerick et. al. in prep).
The the gas mass converted to stars in a time step, $dt$, is
\begin{equation}
M_{ {\rm gas} \to *} = \epsilon_{\rm f} M_{\rm gas} \frac{dt}{\tau_{\rm ff}}.
\end{equation}
In practice, $dt/\tau_{\rm ff} \ll 1$, and $M_{ {\rm gas} \to *}$ is smaller than the minimum star particle mass at parsec scale resolution. We therefore allow star formation to proceed stochastically, following the methods in \cite{Goldbaum2015, Goldbaum2016}, modified for variable stellar masses. In each cell that could potentially form stars, we compute the probability that 100 M$_{\odot}$ of gas will be converted into stars in that time step, and use a random number draw to determine whether or not star formation actually occurs. If it does, we random sample over the adopted IMF until 100 M$_{\odot}$ of stars form, keeping last sampled particle if the total stellar mass formed exceeds 100 M$_{\odot}$. We make the simple assumption of a Salpeter IMF \citep{Salpeter1955} with $\alpha = 2.35$, sampling over a minimum stellar mass of 1 M$_{\odot}$ and maximum stellar mass of 100 M$_{\odot}$.

Formed stars are deposited with random positions within the star forming cell and assigned velocities equal to the cell bulk velocity with a 1~km~s$^{-1}$ velocity dispersion. Stars are assigned metallicities corresponding to the metallicity of the star forming zone, and are chemically tagged with 17 individual species abundances (H, He, and the 15 metals) we follow in our simulations. Stars evolve throughout the simulation, losing mass from stellar winds and supernovae as described below, and by changing types, but persist throughout the entire simulation. For example, low mass stars are tagged as white dwarfs at the end of their life, which may eventually explode as a Type Ia supernova (discussed below), after which they persist as massless tracer particle ``remnants''.

@@

Following the initialization procedure of \cite{Hu2017}, we use artificial supernova driving to generate realistic densities and turbulent properties in the galaxy ISM. This additionally prevents an otherwise uniform collapse of the gas disk. The supernovae explode at a fixed rate of $0.4$~Myr$^{-1}$, corresponding to the SFR obtained given the central HI surface density and the relation presented in \citep{Roychowdhury2009}. We stop the artificial driving 25~Myr after the first star particle forms. These artificial supernova do not drive chemical evolution of the galaxy; their metal yields correspond to the mean ISM abundances.

@@

\subsection{Morphological Structure}
\label{sec:structure}

We begin by characterizing the morphological properties of our dwarf galaxy, as demonstrated in a series of face-on and edge-on images over the simulation time, presented in Figure~\ref{fig:panel_x} and Figure~\ref{fig:panel_z}. Each figure gives density weighted projections of number density (first row), temperature slices (second row), HI column density projections (third row), and O column density projections (fourth row), at four different times in the simulation \textit{(list times here)}. In addition, the number density plots show all main sequence stars in the simulation at the given time, represented by individual black points. \textit{(discuss properties and any interesting characteristics here)}

\begin{figure*}
\centering
\includegraphics[width=0.975\linewidth]{multiplot_4x4_x.png}
\caption{Edge on projections (placeholder)}
\label{fig:panel_x}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=0.975\linewidth]{multiplot_4x4_z.png}
\caption{Face on projections (placeholder)}
\label{fig:panel_z}
\end{figure*}

@@

\textit{ Give plots here showing SFR + SNR, HI mass evolution, and stellar mass evolution. Would be nice to combine this somehow into as few plots as possible. Discuss evolution (this is likely the largest change with simulation time (will we hit a quiescent period??))}

@@

@@

Recent works expect large outflows from low mass dwarf galaxies, with mass loading factors on order of 10 - 1000 (cite fire etc.). Comparatively, Hu et. al. find more modest mass loading factors for their dwarf galaxies, simulated with a comparable set of detailed feedback physics, though in a more massive dwarf galaxies, as this work. In Figure~\ref{fig:mass_loading} we present the mass outflow and mass loading rates for our dwarf galaxy as a function of time, computed at five different positions from the galaxy. We follow \cite{Muratov2015} in defining our mass outflow, taking the outflow rate at any given radius to be the sum of the outflow rate in all cells in a spherical annulus of width $dL$ centered at that radius, or $\dot{M}_{\rm outflow} = \sum M_{\rm gas} \times v_{\rm r} / dL$. We choose $dL = 0.1 R_{\rm vir}$, or 2.74 kpc.

The total mass outflow rates and mass loading factors at 0.1, 0.25, 0.5, and 1.0 R$_{\rm vir}$ are shown in Figure~\ref{fig:mass_outflow}. We use the 10 Myr averaged SFR to compute the mass loading rates. The outflow rate at 0.1 R$_{\rm vir}$ is high, corresponding to mass loading factors on order of 50 - 100 throughout the simulation time. This quickly declines towards larger radii, however, with effectively zero outflow past the virial radius. \cite{Muratov2015} finds typical mass loading factors at 0.25 R$_{\rm vir}$ on order of 20-40 for galaxies with $v_{c} = 30$ km s$^{-1}$ at low redshift. Our dwarf galaxy exhibits mass loading factors between 4 and 40 at this radius; this is consistent with the results from \cite{Muratov2015}, but perhaps slightly below the typical values. Interestingly, the v$_{\rm c}$ $\sim$ 30 km s$^{-1}$ halos examined in \cite{Muratov2015} are more massive than the M$_{\rm vir} = 2.5\times 10^9$ M$_{\odot}$ halo examined here by a factor of a few. Using a fit provided in \cite{Muratov2015} to extrapolate and compare at fixed halo mass, one would expect mass loading factors on order of 100 at 0.25 R$_{\rm vir}$ for our dwarf galaxy, a factor of a few lower than what we find. These differences could be attributed to our lack of cosmological evolution in these isolated simulations, but ultimately requires a larger set of dwarf galaxy simulations to make a more robust comparison. We note, however, that our results are much closer to the \citep{Muratov2015} results than those in \cite{Hu2016,Hu2017}, which find mass loading factors at 0.05 R$_{\rm vir}$ between 1 and 10 for a dwarf galaxy with M$_{\rm vir} = 10^10$ M$_{\odot}$.

% figure here of mass loading and mass outflow rates
\begin{figure*}
\centering
\includegraphics[width=0.45\linewidth]{total_mass_outflow}
\includegraphics[width=0.45\linewidth]{total_mass_loading}
\caption{Spherical mass outflow rates and mass loading rates over time at 4 different radii from the galaxy.}
\label{fig:mass_outflow}
\end{figure*}

Detailed outflow properties, beyond outflow rates and mass loading factors, are important discriminators between the model dependent feedback physics included in galaxy simulations. (this has been shown previously with XX XX XX producing very different outflow properties depending on what physics is included). In Figure~\ref{fig:outflow_velocity} we present radial velocity distributions of all material outside our dwarf galaxy's disk, and within the halo, broken into three gas phases. Half of the outflow, by mass, is at velocities below 40 km s$^{-1}$, with 75\% at velocities of 70 km s$^{1}$ or below. This gas is dominated by the two warm gas phases, with the WNM dominating at lower velocities, and the WIM at higher velocities. The distribution has a very long tail out to and beyond 500 km s$^{-1}$. These dominant launching mechanism in this simulation are supernovae (Emerick et. al. in prep), generating a rapidly moving and volume filling HIM. However, as shown the HIM comprises very little of the outflow by mass. Most of the outflowing gas comes from the warm phase, pushed out by the high pressure, fast moving HIM. Some of this warm gas certainly originates from adiabatically and radiatively cooled HIM, however. The amount of transfer between phases in the halo of our galaxy will be investigated in future work.

@@

@@

\begin{figure}
\includegraphics[width=0.45\linewidth]{phase_diagram.png}
\caption{The full-box temperature vs. number density phase diagram of our dwarf galaxy simulation, averaged over the final 50 Myr of simulation time.}
\label{fig:phase}
\end{figure}

@@

\begin{figure*}
\centering
\includegraphics[width=0.45\linewidth]{mass_fraction_evolution.png}
\includegraphics[width=0.45\linewidth]{volume_fraction_evolution.png}
\caption{The evolution of the mass and volume fractions for each phase of our galaxy's ISM. This figures only consider gas present within the disk of the galaxy.}
\label{fig:ISM_evolution}
\end{figure*}

\subsection{Interstellar Radiation Field}
\label{sec:ISRF}

The ISRF of our galaxy varies dramatically in both space and time. This is not surprising in the low star formation rate regime, where at any given point in space or time there are only a few massive, radiating stars. In Figure~\ref{fig:ISRF} we present 1D volume averaged radial profiles of the ISRF in various bands, time averaged over the last 50 Myr of simulation time. The top panel shows the average $G_{\rm o}$, or the ISRF flux between 6 - 13.6 eV normalized to the value in the solar neighborhood of the Milky Way (see Section XX). The contribution from the metagalactic background is below the lower vertical axis limit on this plot. The shaded region gives the minimum and maximum value of $G_{\rm o}$ in the sampled time range. As shown, regions typically experience fluctuations of an order of magnitude across the galaxy of the ISRF. Interestingly, the central 200 pc does not contain the peak of the ISRF in the galaxy. This is likely a transient property of the galaxy, however, and is a by-product of the inside-out star formation of this dwarf galaxy. By the end of the simulation the feedback from stars produced in the central region has reduced the SFR compared to outer parts of the galaxy. The latter is thus host to more radiating young stars.

\begin{figure}
\includegraphics[width=0.95\linewidth]{G_o_profile} \\
\includegraphics[width=0.95\linewidth]{ionizing_photon_profile}
\caption{1D radial profiles of the ISRF in our galaxy in three different bands, time-averaged over the final 50 Myr of simulation time. The top panel gives $G_{\rm o}$, or the flux of radiation between 6 - 13.6 eV normalized to the value in the solar neighborhood, shaded between minimum and maximum values at each position. The bottom panel gives the HI and HeI ionizing stellar radiation flux, showing average value and maximum values only. For these fields the minimum value reaches zero at some point over the examined period at all radii.}
\label{fig:ISRF}
\end{figure}

The bottom panel gives the ionizing photon fluxes (HI and HeI) from ionizing photons from the stellar radiation \texttt{only}. Since these fields are tracked directly with ray-tracing radiative transfer, the profiles encode information about local attenuation of these photons from dense, neutral gas. This is the main driver of the differences between these fields and $G_{\rm o}$. In addition, we only show the average line and shade to the maximum value at any given position, since the minimum value reaches zero at all radii at some point over the 50 Myr examined. As shown, this causes the profile to vary much more dramatically at all radii. However, the same general trend is preserved of less radiation in the inner 200 pc than the region between 200 and 400 pc. The rapid drop off beyond 400 pc is due to the rapid attenuation of ionizing photons by the cold gas at large radii (see Figure~\ref{fig:panel}).

\begin{figure*}
\centering
\includegraphics[width=0.45\linewidth]{g_o_2D_phase}
\includegraphics[width=0.45\linewidth]{q_o_2D_phase}
\caption{\textbf{THESE PLOTS ARE SINGLE SNAPSHOT PLACEHOLDERS, AND NOT TIME AVERAGED} Time averaged 2D radial profile plots of the ISRF in two flux bands, $G_{\rm o}$ and HI ionizing radiation, illustrating the full dynamic range of radiation flux at a given radius in the galaxy. Here, we include all gas within 25 pc of the midplane of our dwarf galaxy. We note the large difference in color scale between the two plots. Since a majority of the mass of the galaxy is in the cold phase (see Figure~\ref{fig:phase}), and is therefore optically thick to HI ionizing radiation, it does not show up in the HI ionizing radiation diagram. This gas readily appears in the $G_{\rm o}$ since we assume it to be optically thin, though do apply a localized shielding approximation.}
\label{fig:ISRF}
\end{figure*}

These plots are useful to understand the time-varying properties of the ISRF in a spatially averaged sense. However, the local variations for individual regions can be much larger than is illustrated in these profiles. In Figure~\ref{fig:ISRF_2D} we present a 2D profile of $G_{\rm o}$ averaged over the final 50 Myr of the simulation time, which effectively captures the large spikes in local ISRF from recent star forming regions. The 1D profiles accurately capture the averaged heating / ionizing effects of the ISRF in our galaxy, which helps reduce star formation by increase the thermal pressure support and equillibrium temperature of the ISM, yet it is these spikes that act as important local feedback to shut off star formation in dense, collapsing regions that satisfy our star formation criteria.
